Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-13 paper.tex
add further remarks about 75%/100% goals

We believe that this project meets our 75\% goal very solidly, but falls short of the 100\% goal. The primary obstacle to finishing the 100\% goal was that we underestimated the amount of time it would take to clear up bugs relating to network byte order, which were the source of much debugging time. While we believe that adding caching would not be particularly difficult, given the structure of our nameserver, there simply was not enough time to do so.

>>>>

We believe that this project meets our 75\% goal very solidly, but
falls short of the 100\% goal.\footnote{Our 75\% goal was to simply implement
  a working \Kwd{DNS} server; our 100\% goal was to extend this basic
  server with support for caching, and for further resource record
  types; we would also have liked to support compressing domain
  names. In our implementation, we supported only \emph{decompressing}
  domain names, which is allowed by the \Kwd{DNS} specification, but
  is not optimal~\citep{rfc:1035}.} The primary obstacle to finishing
the 100\% goal was that we underestimated the amount of time it would
take to clear up bugs relating to network byte order, which were the
source of much debugging time. While we believe that adding caching
would not be particularly difficult, given the structure of our
nameserver, there simply was not enough time to do so.
